---
title: "linear model from Web"
author: "Roxan Barakat"
date: "Spring 2023"
output:
   html_document:
         toc: true
         toc_depth: 5
        
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Read about the data from the website where it is staged.  Then form three regression models; Model1 is SIMS~ARM, Model2 is SIMS~GRIP, and Model3 is SIMS~ARM+GRIP. For each model find a 95% prediction interval of SIMS given a value of 94  for GRIP and 88 for ARM. Compare Model1 with Model3 using anova. Write it up in a markdown document, push the project up to your github account and submit it back to canvas as link. 

 


```{r include=FALSE}
require(tidyverse)
require(tigerstats)
require(rgl)
require(knitr)

```

```{r}
data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)  

```

## Model 1 SIM~ARMS

### scatterplot
```{r}
basicNN <- ggplot(data,aes(y=SIMS,x=ARM))
```

```{r}
basicNN + geom_point() + ggtitle("SIMS vs ARM") + theme(plot.title = element_text(hjust = 0.5, size = 20))
```
This data shows the simulation expectation of arm strength in the workers. This tells us that it is expected for most of the population to have a strength between 50 and 100 for arm strength. 

### Numerical results
```{r}
cor(SIMS~ARM,data=data)
```
The larger the number we get, the larger the correlation between the two is. From this data, we can see that there is a small correspondence between the two since the number is approaching 1. 

### Inferential  (Build model.1)
```{r}
model.1 <- lm(SIMS~ARM,data=data)
summary.lm(model.1)
```
The equation for the line of this scenario is SIMS = 0.054563xARM-4.095160. Since we have a positive coefficient, the line increases making it move from the lower left corner to the upper right corner. 

#### Predict at target point


#### scatterplot with model fit
  

## Model 2 SIM~GRIP

### Now add in scatterplot


### Numerical results 


### Inferential  (Build model.2)
  

#### predict model.2 at target point

#### now add the model fit to our plot for model.2
  


## Model 3 SIM~ARM+GRIP

### Numerical results (cor)

`
  
### Inferential  (Build 2-dimentional model.3)

#### predict model.3 at target point
  

## Comparing nested models ANOVA Test

### Model.1 vs Model.3
### Model.2 vs Model.3

## Informally compare Model.1 with model.2

