---
title: "linear model from Web"
author: "Roxan Barakat"
date: "Spring 2023"
output:
   html_document:
         toc: true
         toc_depth: 5
        
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Read about the data from the website where it is staged.  Then form three regression models; Model1 is SIMS~ARM, Model2 is SIMS~GRIP, and Model3 is SIMS~ARM+GRIP. For each model find a 95% prediction interval of SIMS given a value of 94  for GRIP and 88 for ARM. Compare Model1 with Model3 using anova. Write it up in a markdown document, push the project up to your github account and submit it back to canvas as link. 

 


```{r include=FALSE}
require(tidyverse)
require(tigerstats)
require(rgl)
require(knitr)

```

```{r}
data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)  

```

## Model 1 SIM~ARMS

### scatterplot
```{r}
basicNN <- ggplot(data,aes(y=SIMS,x=ARM))
```

```{r}
basicNN + geom_point() + ggtitle("SIMS vs ARM") + theme(plot.title = element_text(hjust = 0.5, size = 20))
```
This data shows the simulation expectation of arm strength in the workers. This tells us that it is expected for most of the population to have a strength between 50 and 100 for arm strength. 

### Numerical results
```{r}
cor(SIMS~ARM,data=data)
```
The larger the number we get, the larger the correlation between the two is. From this data, we can see that there is a small correspondence between the two since the number is approaching 1. 

### Inferential  (Build model.1)
```{r}
model.1 <- lm(SIMS~ARM,data=data)
summary.lm(model.1)
```
The equation for the line of this scenario is SIMS = 0.054563xARM-4.095160. Since we have a positive coefficient, the line increases making it move from the lower left corner to the upper right corner. 

#### Predict at target point
```{r}
tgtpoint=data.frame(ARM=88, GRIP=94)

predict(model.1, tgtpoint, interval = c("prediction"))
```
The table shows that our predicted target plot is 0.7063836 but 95% of the time, we are going to have a value between -1.726209 and 3.13897.

#### scatterplot with model fit
```{r}
basicNN + geom_point() + ggtitle("SIMS vs ARM") + theme(plot.title = element_text(hjust = 0.5, size = 20)) + geom_smooth(method = lm)
``` 
The data  above shows us the line of best fit from the data points collected from SIMS vs ARM. This shows which data points are the closest to the expected results. 
## Model 2 SIM~GRIP

### Now add in scatterplot
```{r}
basicGRIP <- ggplot(data,aes(y=SIMS,x=GRIP))
```
```{r}
basicGRIP + geom_point() + ggtitle("SIMS vs GRIP") + theme(plot.title = element_text(hjust = 0.5, size = 20))
``` 

### Numerical results 
```{r}
cor(SIMS~GRIP, data=data)
```
For SIMS vs GRIP we have a value of 0.6398458 but for the SIMS vs ARM we got a 0.6860073. The value of SIMS vs ARMS is a higher value than that of SIMS vs GRIP making the correspondence slightly smaller in the correlation of data tables. This shows us that the SIMS vs ARM model is more accurate than the SIMS vs GRIP model. 

### Inferential  (Build model.2)
```{r}
model.2 <- lm(SIMS~GRIP, data=data)
summary.lm(model.2)
```
The data above gives us an equation of SIMS= 0.045463x GRIP -4.809675 as the equation for our line of best fit. With the positive coefficient we have a positive slope for the line making it start in the bottom left corner and travel towards the top right hand corner. 

#### predict model.2 at target point
```{r}
predict(model.2, tgtpoint, interval = c("prediction"))
```
The table shows that our best fit value for this scenario is 0.536154, but 95% of the time the value will be between -3.107961 and 2.035652.

#### now add the model fit to our plot for model.2
  


## Model 3 SIM~ARM+GRIP

### Numerical results (cor)

`
  
### Inferential  (Build 2-dimentional model.3)

#### predict model.3 at target point
  

## Comparing nested models ANOVA Test

### Model.1 vs Model.3
### Model.2 vs Model.3

## Informally compare Model.1 with model.2

